Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
forward access path defined.

In summary, the equations generated during liveness analysis are:
\begin{enumerate}
\item For each function $\mathit{f}$, equations defining \Df{f}{i} for
  use by \Lfonly$_{\mathit f}$.
\item For each function $\mathit{f}$, an equation defining the summary
  demand $\sigma_{\mathit f}$ on $e_f$.
\item  For  each  function   $\mathit{f}$  (including  $\mainpgm$  for
  $e_\mainpgm$)  an equation  defining liveness  at each  GC point  of
  $e_{\mathit f}$.
\end{enumerate}
\subsection{Solving liveness equations---the grammar
interpretation}\label{sec:grammar-formulation}
The  equations above can now be re-interpreted as a
context-free grammar (CFG)  on the alphabet $\lbrace\acar, \acdr,
\bcar, \bcdr, \clazy\rbrace$.  Let  \var{$X$} denote the non-terminal
for
a variable  $X$ occurring on  the LHS of the  equations generated
from the analysis.  We can  think of the resulting productions as
being associated with several  grammars, one for each non-terminal
\var{\Lanv{i}{x}} regarded as a start symbol.  As an example, the
grammar    for   \var{\Lanv{1}{\xl}}   comprises    the   following
productions:
\begin{eqnarray*}
  \var{\Lanv{1}{\xl}}  &\rightarrow& 
  \clazy\var{\sigma_{\length}} \mid \acdr \var{\Df {\length}{1}}{\clazy\var{\sigma_{\length}}}  \\
  & & \mid
  \clazy\var{\Df{\length}{1}}{\clazy\var{\sigma_{\length}}} \\
  \var{\Df{\length}{1}} &\rightarrow& \clazy \mid
  \acdr\var{\Df{\length}{1}}\clazy
       \mid \clazy\var{\Df{\length}{1}}{\clazy}\\
\langle {\sigma_{\length}} \rangle
&\rightarrow&
\epsilon  \mid \clazy\langle{\sigma_{\length}}\rangle
\end{eqnarray*}
Other equations can be converted similarly.  The language generated by
\var{\Lanv{i}{x}},  denoted $\mathscr{L}(\var{\Lanv{i}{x}}) $,  is the
desired  solution of  \Lanv{i}{x}.  However,  recall from  our earlier
discussion that the decision problem  that we are interested in during
garbage collection at a program point $\pi_i$ is:
\begin{quote}
Let  $x.\alpha$ be  a forward  access  path consisting  only of  edges
\acar\    and   \acdr\    (but    not   \bcar, \bcdr\ or \clazy).     Let
$\mathscr{L}(\var{\Lanv{i}{x}}) \stackrel{*}{\hookrightarrow} \sigma$,
where $\sigma$ consists  of forward paths only. Then  does $\alpha \in
\sigma$?
\end{quote}

>>>>

In summary, the equations generated during liveness analysis are:
\begin{enumerate}
\item For each function $\mathit{f}$, equations defining \Df{f}{i} for
  use by \Lfonly$_{\mathit f}$.
\item For each function $\mathit{f}$, an equation defining the summary
  demand $\sigma_{\mathit f}$ on $e_f$.
\item  For  each  function   $\mathit{f}$  (including  $\mainpgm$  for
  $e_\mainpgm$)  an equation  defining liveness  at each  GC point  of
  $e_{\mathit f}$.
\end{enumerate}
\subsection{Solving liveness equations---the grammar
interpretation}\label{sec:grammar-formulation}
The  equations above can now be re-interpreted as a
context-free grammar (CFG)  on the alphabet $\lbrace\acar, \acdr,
\bcar, \bcdr, \clazy\rbrace$.  Let  \var{$X$} denote the non-terminal
for
a variable  $X$ occurring on  the LHS of the  equations generated
from the analysis.  We can  think of the resulting productions as
being associated with several  grammars, one for each non-terminal
\var{\Lanv{i}{x}} regarded as a start symbol.  As an example, the
grammar    for   \var{\Lanv{1}{\xl}}   comprises    the   following
productions:
\begin{eqnarray*}
  \var{\Lanv{1}{\xl}}  &\rightarrow& 
  \clazy\var{\sigma_{\length}} \mid \acdr \var{\Df {\length}{1}}{\clazy\var{\sigma_{\length}}}  \\
  & & \mid
  \clazy\var{\Df{\length}{1}}{\clazy\var{\sigma_{\length}}} \\
  \var{\Df{\length}{1}} &\rightarrow& \clazy \mid
  \acdr\var{\Df{\length}{1}}\clazy
       \mid \clazy\var{\Df{\length}{1}}{\clazy}\\
\langle {\sigma_{\length}} \rangle
&\rightarrow&
\epsilon  \mid \clazy\langle{\sigma_{\length}}\rangle
\end{eqnarray*}
Other equations can be converted similarly.  The language generated by
\var{\Lanv{i}{x}},  denoted  $\mathscr{L}(\var{\Lanv{i}{x}})$, is  the
desired solution  of \Lanv{i}{x}.  However,  note that the  strings in
the  language are  over alphabet  $\lbrace \acar,  \acdr,\bcar, \bcdr,
\clazy \rbrace$, but  we want {\em forward} access paths  only, i. e.,
access paths over the alphabet $\lbrace \acar, \acdr \rbrace$. In
other words,  the decision  problem that we  are interested  in during
garbage collection at a program point $\pi_i$ is:
\begin{quote}
Let  $x.\alpha$ be  a forward  access  path consisting  only of  edges
\acar\    and   \acdr\    (but    not   \bcar, \bcdr\ or \clazy).     Let
$\mathscr{L}(\var{\Lanv{i}{x}}) \stackrel{*}{\hookrightarrow} \sigma$,
where $\sigma$ consists  of forward paths only. Then  does $\alpha \in
\sigma$?
\end{quote}
